Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
revised sec 4 (synthesis elements specific to control)

\paragraph{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some domain
$\mathcal{D}$.

@@

\paragraph{Synthesis elements specific to control systems}

Next, we describe the specific property that we pass to the program
synthesiser as the specification $\sigma$.  There are two different
algorithms in DSVerifier that can be used for stability
verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on
Schur's decomposition and another one based on Jury's
criteria~\cite{astrom1997computer}.  Here, we choose Jury's
method~\cite{astrom1997computer}, due to its efficiency.

@@

\red{[clear elucidation of the mapping between this and the domains used 
in the general description of the synthesiser]}

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below at $I_b=16,F_b=24$,
which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
   ([xshift=6.7cm]aux2) edge node[align=center] {Reset} (aux1);

>>>>

\subsection{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.

@@

\subsection{Synthesis elements specific to control systems}

\paragraph{Property specification}
Next, we describe the specific property that we pass to the program
synthesiser as the specification $\sigma$.  There are two different
algorithms in DSVerifier that can be used for stability
verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on
Schur's decomposition and another one based on Jury's
criteria~\cite{astrom1997computer}.  Here, we choose Jury's
method~\cite{astrom1997computer}, due to its efficiency.

@@

%% \red{[clear elucidation of the mapping between this and the domains used 
%% in the general description of the synthesiser]}

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.  
\cdsay{integrate sec 2.4 with Dario}

In the {\sc verify} phase, we have a two-step process. 
First, in the {\sc Uncertainty} sub-phase, assuming the 
current precision \param{I_b}{F_b},
we check whether 
the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

If the result of the {\sc Uncertainty} verification is that
$\neg \phi_{stability}$ is unsatisfiable for $S(z)$, then we pass 
the current candidate solution to the {\sc Precision} verification sub-phase, 
which checks the propagation of the error in the fixed-point 
calculations. If this check returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.

\subsection{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below at $I_b=16,F_b=24$,
which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
